An Experimental Analysis of the Influence of the Precision of Parameters in an Artificial Neural Network

### 2025-07-16 paper/main.tex
almost done

\begin{figure}[H]
	\centering
	\includegraphics[width=0.85\textwidth]{figures/FP16_32_clipping.png}
	\caption{Affect of Gradient Norm on accuracy, training and testing timings.
		Accuracy is virtually the same between FP16 and FP32 when gradient clipping is used
		validating the stability of AMP and gradient scaling.
		Eval time is nearly identical for both formats, as evaluation involves fewer operations
		and less intense memory bandwidth usage.}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.85\textwidth]{figures/gradclip_16.png}
	\caption{Effect of Per-Element Gradient Clipping on FP16.
		Accuracy vs Training & Eval Time}
	\label{fig:grad16}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.85\textwidth]{figures/gradclip_32.png}
	\caption{Effect of Per-Element Gradient Clipping on FP32.
		Accuracy vs Training & Eval Time}
	\label{fig:grad32}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.85\textwidth]{figures/118_dist2.png}
	\caption{Distribution of model weights in each layer after rounding to two decimals.
		This appears to be a good approximation already.}
	\label{fig:118_2}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.85\textwidth]{figures/118_accuracy.png}
	\caption{Test Accuracy vs.\ number of decimal digits retained in weights.}
	\label{fig:118_acc}
\end{figure}

>>>>

\begin{figure}[H]
	\centering
	\includegraphics[width=0.95\textwidth]{figures/FP16_32_clipping.png}
	\caption{Affect of Gradient Norm on accuracy, training and testing timings.
		Accuracy is virtually the same between FP16 and FP32 when gradient clipping is used
		validating the stability of AMP and gradient scaling.
		Eval time is nearly identical for both formats, as evaluation involves fewer operations
		and less intense memory bandwidth usage.}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.95\textwidth]{figures/gradclip_16.png}
	\caption{Effect of Per-Element Gradient Clipping on FP16. Accuracy vs Training \& Eval Time}\label{fig:grad16}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.95\textwidth]{figures/gradclip_32.png}
	\caption{Effect of Per-Element Gradient Clipping on FP32. Accuracy vs Training \& Eval Time}\label{fig:grad32}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.85\textwidth]{figures/118_dist2.png}
	\caption{Distribution of model weights in each layer after rounding to two decimals.
		This appears to be a good approximation already.}\label{fig:118_2}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.85\textwidth]{figures/118_accuracy.png}
	\caption{Test Accuracy vs.\ number of decimal digits retained in weights.}\label{fig:118_acc}
\end{figure}
